Reducing the Memory Cost of Training Convolutional Neural Networks by CPU Offloading

### 2019-07-10 article.tex
Last modifications

% Describe system setup.
We conduct our experiments on a workstation with an NVIDIA Titan X GPU connected 
to the host through XXX PCIe lanes, which represents a peak bandwidth of XXXB/s.
We believe this set-up to be representative of a typical workstation for individual practitioners, 
if not slightly unfavorable, as our device to host bandwidth is rather limited.
Unless specified otherwise, we conduct our experiments on a batch of 32 RGB images 
with a resolution of 128 by 128 pixels.
For each experiment, we are interested in the total memory usage and Wall time of
the computation for a full training iteration including the forward and backward pass through the network.
It is important to note that our method does not modify the actual computations performed
by the network so that the training dynamics and accuracy are unaffected by CPU Offloading.
Hence, we focus on reporting the memory vs. wall time trade-off,
 as the accuracy reached by the model is strictly unaffected.

@@

\begin{table*}[h]
\begin{center}
\begin{tabular}{ c c c}	
\hline
Operation                   & Time (ms)  & Rel. Improvement\\
\hline
Baseline                    &  $560$    & $0\%$      \\
Pinned Memory               &  $355$    & $-xxx\%$ \\
Parallelization             &  $236$    & $-xxx\%$ \\
\hline
\end{tabular}
\caption{Speed-ups achieved by the pinned memory buffers and parallelization techniques}
\end{center}
\end{table*}

>>>>

% Describe system setup.
We conduct our experiments on a workstation with an NVIDIA Titan X GPU connected 
to the host through PCIe1 16x lanes, which represents a peak bandwidth of 6.5 GB/s.
We believe this set-up to be representative of a typical workstation for individual practitioners, 
if not slightly unfavorable, as our device to host bandwidth is rather limited.
Unless specified otherwise, we conduct our experiments on a batch of 32 RGB images 
with a resolution of 128 by 128 pixels.
For each experiment, we are interested in the total memory usage and Wall time of
the computation for a full training iteration including the forward and backward pass through the network.
It is important to note that our method does not modify the actual computations performed
by the network so that the training dynamics and accuracy are unaffected by CPU Offloading.
Hence, we focus on reporting the memory vs. wall time trade-off,
 as the accuracy reached by the model is strictly unaffected.

@@

\begin{table*}[h]
\begin{center}
\begin{tabular}{ c c c}	
\hline
Operation                   & Time (ms)  & Rel. Improvement\\
\hline
Baseline                    &  $560$    & $0\%$      \\
Pinned Memory               &  $355$    & $-36.6\%$ \\
Parallelization             &  $236$    & $-21.2\%$ \\
\hline
\end{tabular}
\caption{Speed-ups achieved by the pinned memory buffers and parallelization techniques}
\end{center}
\end{table*}
